### 2022-07-30 paper/akweury/document.tex
update an2 model

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
		\caption{GT}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.image0.png}
		\caption{GCNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
		\caption{CNN}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
		\caption{NOC}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
		\caption{SVD}
	\end{subfigure}	
	\caption{Surface Normal Inference based GCNN model on "Dragon´´ object. The first row shows the estimated surface normal. The second row is the angle error map.}
	\label{fig:gcnn-eval}
\end{figure}

>>>>

	\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.depth0_noise.png}
\end{subfigure}
\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.depth0_noise.png}
\end{subfigure}
\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.depth0_noise.png}
\end{subfigure}
\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.depth0_noise.png}
\end{subfigure}
\begin{subfigure}[b]{0.18\linewidth}
	\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.depth0_noise.png}
\end{subfigure}

	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05051.image0.png}
		\caption{Baoshanlu}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05109.image0.png}
		\caption{Vase}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05111.image0.png}
		\caption{Garfield}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05113.image0.png}
		\caption{Dragon}
	\end{subfigure}
	\begin{subfigure}[b]{0.18\linewidth}
		\includegraphics[width=\linewidth]{./Figures/test_scenes/05126.image0.png}
		\caption{Bus}
	\end{subfigure}	
	\caption{Some of the test scenes during the training. From top to bottom, normal map, depth map, noised depth map, grayscale image.}
	\label{fig:test-scene}
\end{figure}
